---
title: "Style guide to R Markdown"
author: "Thiyanga Talagala"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Visualization

Data visualization is the graphical representation of information and data. This is important because it allows relationships of the data, trends and patterns to be more easily seen.

##  Data Description: `iris`

The Iris flower data set (also known as Fisher’s Iris data set) is a multivariate data set introduced by the British statistician, eugenicist, and biologist Ronald Fisher.

```{r, fig.height=3} 
library(ggplot2)
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species)) + 
  geom_point() + 
  coord_fixed(ratio=1.7) + 
  scale_color_brewer(palette = "Dark2")
```



### Scatter plot

A scatter plot (aka scatter chart, scatter graph) uses dots to represent values for two different numeric variables.

# Statistical modelling

Major resource for statistical modelling

- broom

- tidyverse/ modelr


